A generalized model for the charge transport properties of dressed quantum Hall systems

### 2022-01-21 paper/submission3/manuscript/dressed_quantum_hall_sub3.tex
Finalize paper

In contrast, we can observe more exciting phenomena by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport.
Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIROs) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
{\color{Red}
This inspired investigations on the theoretical description of MIROs and several semi-classical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}. These formalisms provide a proper explanation for the experimental observations of MIROs. However, these experimental and theoretical works have been linked to the effects of low-frequency (microwave) electromagnetic fields that increase the longitudinal conductivity.
In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system leads to different behavior that reduces the longitudinal conductivity \cite{dini16}.
Since high-frequency radiation only contributes to the suppression of electron scattering, the driving field can be treated as a pure dressing (non-absorbable) field \cite{dini16}.
Thus, the influence induced by a high-frequency pure dressing field on
magneto-transport properties of 2DEG quantum Hall system need to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.}
Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall system subjected to a high-frequency field.
However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
The authors of Ref. \cite{dini16} used the conductivity models from Refs. \cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.

@@

{\color{Red} To further evaluate the conductivity expression, we must specify the distribution function. Generic interacting Floquet systems absorb photons from the radiation and tend to heat \cite{seetharam2019,rudner2020}.

@@

\end{equation}}Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(\ref{eq:31}) leads to

@@

Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered various remarkable
magneto-transport properties induced by microwave radiation on 2DEG quantum Hall systems.
{\color{Red}
However, these experiments and theoretical models only analyzed the behavior of MIROs in 2DEG systems which are based on low-frequency fields.}
It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field.
{\color{Red}
In our case, the applied dressing field is in the high-frequency regime where we can neglect the photon interactions. The only influence of the electromagnetic field is the suppression of electron scattering.}
This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum Hall systems. Therefore, our theoretical analysis can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
%===============================================================================

@@

  {201311} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%

@@

  \citenamefont {Smet}, \citenamefont {von Klitzing}, \citenamefont

@@

  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {von Klitzing}}, \bibinfo

@@

  \citenamefont {Smet}, \citenamefont {Von~Klitzing}, \citenamefont

@@

  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Von~Klitzing}}, \bibinfo

@@

  {\bibfnamefont {W.}~\bibnamefont {Johnson}},\ and\ \bibinfo {author}

@@

  {Mancoff}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Zielinski}},
  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Marcus}}, \bibinfo

@@

  {\bibfnamefont {A.}~\bibnamefont {Gossard}},\ }\href

@@

@@

  {A.}~\bibnamefont {Morpurgo}},\ and\ \bibinfo {author} {\bibfnamefont

@@

  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Kawaguchi}}, \bibinfo
  {author} {\bibfnamefont {M.}~\bibnamefont {Endo}}, \bibinfo {author}
  {\bibfnamefont {M.}~\bibnamefont {Saeki}},\ and\ \bibinfo {author}

>>>>

In contrast, we can observe more exciting phenomena by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport.
Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIROs) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
This inspired investigations on the theoretical description of MIROs and several semi-classical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}. These formalisms provide a proper explanation for the experimental observations of MIROs. However, these experimental and theoretical works have been linked to the effects of low-frequency (microwave) electromagnetic fields that increase the longitudinal conductivity.
In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system leads to different behavior that reduces the longitudinal conductivity \cite{dini16}.
Since high-frequency radiation only contributes to the suppression of electron scattering, the driving field can be treated as a pure dressing (non-absorbable) field \cite{dini16}.
Thus, the influence induced by a high-frequency pure dressing field on
magneto-transport properties of 2DEG quantum Hall system need to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.
Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall system subjected to a high-frequency field.
However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
The authors of Ref. \cite{dini16} used the conductivity models from Refs. \cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.

@@

To further evaluate the conductivity expression, we must specify the distribution function. Generic interacting Floquet systems absorb photons from the radiation and tend to heat \cite{seetharam2019,rudner2020}.

@@

Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(\ref{eq:31}) leads to

@@

Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered various remarkable
magneto-transport properties induced by microwave radiation on 2DEG quantum Hall systems.
However, these experiments and theoretical models only analyzed the behavior of MIROs in 2DEG systems which are based on low-frequency fields.
It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field.
In our case, the applied dressing field is in the high-frequency regime where we can neglect the photon interactions. The only influence of the electromagnetic field is the suppression of electron scattering.
This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum Hall systems. Therefore, our theoretical analysis can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
%===============================================================================

@@

  {201311(R)} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%

@@

  \citenamefont {Smet}, \citenamefont {vonKlitzing}, \citenamefont

@@

  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {vonKlitzing}}, \bibinfo

@@

  \citenamefont {Smet}, \citenamefont {von~Klitzing}, \citenamefont

@@

  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {von~Klitzing}}, \bibinfo

@@

  {\bibfnamefont {W.~B.}~\bibnamefont {Johnson}},\ and\ \bibinfo {author}

@@

  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.~B.}~\bibnamefont
  {Mancoff}}, \bibinfo {author} {\bibfnamefont {L.~J.}~\bibnamefont {Zielinski}},
  \bibinfo {author} {\bibfnamefont {C.~M.}~\bibnamefont {Marcus}}, \bibinfo

@@

  {\bibfnamefont {A.~C.}~\bibnamefont {Gossard}},\ }\href

@@

  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~D.}~\bibnamefont

@@

  {A.~F.}~\bibnamefont {Morpurgo}},\ and\ \bibinfo {author} {\bibfnamefont

@@

  , \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Endo}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Saeki}},\ and\ \bibinfo {author}
